$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-06 paper/paper.tex
Be more careful with the example derivation

  Let $\func{\omega}$ be a shortcut for $(\one \comma \one)$ in an algebra of shared types.
  Let $\epsilon$ be the empty usage context --- where all usage annotations are $(\zero \comma \zero)$.
  To type $\func{p}$, we need a channel over which we can transmit another channel.
  We therefore create a new channel with usage annotations $(\one \comma \one)$ capable of transmitting data of type $\channel{\unit}{\func{\omega}}$, and declare (with $\li$) that we only transmit input capabilities over it (line 7).
  The left-hand process is typed following its syntax (line 8).
  On the right-hand we need the channel that is going to be sent (line 9).
  The type $\unit$ of this channel is entirely determined by the type $\channel{\unit}{\func{\omega}}$ of the channel over which it is going to be transmitted.
  Its usage annotation is $(\one \comma \one)$: we will transmit $(\one \comma \zero)$ and save $(\zero \comma \one)$ for the continuation process.

  \begin{lstlisting}[label=lst:derivation,mathescape,numbers=left,caption=Typing a process that sends part of one channel over another.]
  $\func{p}$ : $\Process_1$
  $\func{p}$ = $\new{}$
       $(\comp{\recv{\constr{0}} (\recv{\constr{0}} \PO)}$
       ${\new{} (\send{\suc \; \constr{0}} {\constr{0}} (\send{\constr{0}}{\suc \; \suc \; \constr{0}}) \; \PO)})$

  $\func{\_}$ : $\types{\constr{[]} \comma \unit}{\constr{[]} \comma \func{\omega}}{\func{p}}{\epsilon}$
  $\func{\_}$ = $\constr{chan} \; \channel{\unit}{\func{\omega}} \; \li \; \one \; (\constr{comp}$
       $(\constr{recv} \; \constr{0} \; (\constr{recv} \; \constr{0} \; \constr{end}))$
       $(\constr{chan} \; \unit \; \func{\omega} \; \one \; (\constr{send} \; (\suc \; \constr{0}) \; \constr{0} \; (\constr{send} \; \constr{0} \; (\suc \; \suc \; \constr{0}) \; \constr{end})))
       )$
  \end{lstlisting}
\end{example}

>>>>

  Let $\func{\omega}$ be a shortcut for $(\one \comma \one)$ in an algebra of shared types.
  Let $\func{\epsilon}$ be the empty usage context --- where all usage annotations are $(\zero \comma \zero)$.
  To type $\func{p}$, we need a channel over which we can transmit another channel.
  We therefore create a new channel with usage annotations $(\one \comma \one)$ capable of transmitting data of type $\channel{\unit}{\func{\omega}}$, and declare (with $\li$) that we only transmit input capabilities over it (line 7).
  The left-hand process is typed following its syntax (line 8).
  On the right-hand we need the channel that is going to be sent (line 9).
  The type $\unit$ of this channel is entirely determined by the type $\channel{\unit}{\func{\omega}}$ of the channel over which it is going to be transmitted.
  Its usage annotation is $(\one \comma \one)$: we will transmit $(\one \comma \zero)$ and save $(\zero \comma \one)$ for the continuation process.

  \begin{lstlisting}[label=lst:derivation,mathescape,numbers=left,caption=Typing a process that sends part of one channel over another.]
  $\func{p}$ : $\Process_{\suc \constr{zero}}$
  $\func{p}$ = $\new{}$
       $(\comp{\recv{\constr{0}} (\recv{\constr{0}} \PO)}$
       ${\new{} (\send{\suc \; \constr{0}} {\constr{0}} (\send{\constr{0}}{\suc \; \suc \; \constr{0}}) \; \PO)})$

  $\func{\_}$ : $\types{\constr{[]} \comma \unit}{\constr{[]} \comma \func{\omega}}{\func{p}}{\func{epsilon}}$
  $\func{\_}$ = $\constr{chan} \; \channel{\unit}{\func{\omega}} \; \li \; \one \; (\constr{comp}$
       $(\constr{recv} \; \constr{0} \; (\constr{recv} \; \constr{0} \; \constr{end}))$
       $(\constr{chan} \; \unit \; \func{\omega} \; \one \; (\constr{send} \; (\suc \; \constr{0}) \; \constr{0} \; (\constr{send} \; \constr{0} \; (\suc \; \suc \; \constr{0}) \; \constr{end})))
       )$
  \end{lstlisting}
\end{example}
